Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-25 parts/def-ph.tex
move some defs

\subsection{Definition of the Process Hitting with $k$ priorities}
\label{ssec:PH}
\towrite{Reformuler (actuellement trop proche de CMSB)}
A PH (\pref{def:PH}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.

@@

\begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
  A \emph{Process Hitting with $k$ priorities}, where $k \in \sN^*$, is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, where:
  \begin{itemize}
    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of states, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$. Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_k} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_k) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_k \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
  \end{itemize}
  We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
\end{definition}

@@

In \pref{def:cs} and \pref{def:component} we define the notion of well-formed component and cooperative sort.
A sort $a$ is a well-formed component iff
it is hit only by actions of priority $2$.
A cooperative sort $a$ is well-formed iff
it is hit only by actions of priority $1$,
if any sub-state of its neighborhood is represented by at least one local steady state in this sort,
and if any of its processes represents at least one sub-state of its neighborhood.
\begin{definition}
\label{def:component}
  A sort $a \in \PHs$ is said to be a well-formed component iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
  \end{itemize}
\end{definition}
\begin{definition}
  \label{def:cs}
  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) \neq \emptyset$
    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, a_i \in \pfp_s(a)$
  \end{itemize}
\end{definition}

We call $\components$ the set of well-formed components and $\cs$ the set of well-formed cooperative sorts.
We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$

>>>>

\subsection{Definition of the Process Hitting with $k$ priorities}
\label{ssec:PH}
\towrite{Reformuler (actuellement trop proche de CMSB)}
A PH (\pref{def:ph}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.

@@

\begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
\label{def:ph}
  A \emph{Process Hitting with $k$ priorities}, where $k \in \sN^*$, is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, where:
  \begin{itemize}
    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of states, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$. Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_k} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_k) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_k \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
  \end{itemize}
  We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
\end{definition}

@@

In \pref{def:cs} and \pref{def:component} we define the notion of well-formed component and cooperative sort.
A sort $a$ is a well-formed component iff
it is hit only by actions of priority $2$.
A cooperative sort $a$ is well-formed iff
it is hit only by actions of priority $1$,
if any sub-state of its neighborhood is represented by at least one local steady state in this sort,
and if any of its processes represents at least one sub-state of its neighborhood.
\begin{definition}
\label{def:component}
  A sort $a \in \PHs$ is said to be a well-formed component iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
  \end{itemize}
\end{definition}
\begin{definition}
  \label{def:cs}
  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) \neq \emptyset$
    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, a_i \in \pfp_s(a)$
  \end{itemize}
\end{definition}
We call $\components$ the set of well-formed components and $\cs$ the set of well-formed cooperative sorts.
We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$

Finally, we denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
\begin{align*}
  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
\end{align*}
Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.

### 2013-03-25 parts/sa.tex
move some defs

\begin{definition}[Scenario ($\Sce$)]
\label{def:scenario}
  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all scenarios is noted $\Sce$.
\end{definition}

@@

États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
\begin{align*}
  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
\end{align*}
Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.

>>>>

\section{Static analysis}\label{sec:sa}

@@
